\sc Cells at War: The Playfulness of Game-Based Learning

### 2023-03-07 thesis_template/paper0904.tex
March 7, basically done materials and methods

In 2021, the BIO1A03 instructional team partnered up with the George Brown College School of Design, and received support from CEWIL Canada (Co-operative Education and Work-Integrated Learning Canada), formerly known as CAFCE (Canadian Association for Co-operative Education), to create and develop an educational biological video game that could be used in BIO1A03.

@@

@@

>>>>

In 2021, the BIO1A03 instructional team partnered up with the George Brown College School of Design, and received support from CEWIL Canada (Co-operative Education and Work-Integrated Learning Canada), formerly known as CAFCE (Canadian Association for Co-operative Education), to design and implement an educational biological video game that could be used as an instructional and engaging teaching tool in BIO1A03. A small cohort of McMaster Univeristy Biology students and supervising professors, as well as game designers, programmers, animators, audio engineers, and artists from the George Brown College School of Design were selected to pilot this project.

Concept development began in September of 2021. In this phase, students from both institutions worked collaboratively to brainstorm concepts for a biological video game that would be both engaging and educational. The theme for the game was centred around single-gene diseases. Biology students from McMaster University were responsible for selecting and researching a specific single-gene disease. This information was exchanged with students from George Brown College, who in-turn provided a wealth of knowledge on how to turn these static, difficult to understand concepts into engaging gameplay mechanics. Students pitched these proposals to supervising professors who then selected the ideas and game elements that best suited the goals of the project.

The game production phase then began in November of 2021. Students from George Brown College started bringing these ideas to life through artwork, animation, and programming. McMaster Biology students served as subject matter experts, ensuring scientific accuracy throughout the production process, as well as creating an encyclopedia of important biological concepts that were highlighted in-game. Throughout the production stage, weekly online meetings were held to keep all members updated with progress. Discord was also utilized throughout the entire process in order to ensure open dialogue between students and supervisors, as well as to share game assets and important information. A functioning build of the game was completed in late March of 2021, and was introduced in the final BIO1A03 class of the winter 2021 semester, in place of lecture material. After class, students were asked to complete a survey regarding their attitudes towards the game.

@@

Students qualifying for participation in the survey included only those enrolled in the winter 2021 semester of BIO1A03. Students were informed about the survey prior to playing the game, through both in-class and online announcements posted on Desire to Learn. Students who did not complete the survey were informed that this would not effect course performance. Those who participated were incentivized by being entered into a draw to win prizes.

@@

The survey was developed and delivered through the LimeSurvey\textregistered \space platform. Students were asked a total of 14 questions regarding opinions and attitudes on their current undergraduate education, as well as feedback on game-based learning in the biology classroom. The National Survey of Student Engagement (NSSE) was used as a framework to generate the questions that were asked. NSSE questions assess the extent to which students engage in educational practices in the context of higher levels of learning (NSSE website citation). MORE HERE ABOUT NSSE...
